---
title: "Monetary Incentives"
author: "Wai Tak Tung"
date: "4/6/2022"
output: pdf_document
 :keep_md = TRUE
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
install.packages('MASS')
install.packages('ggplot2')
library(ggplot2)

## Haas et al (2021) Diminishing marginal effect visualisation
eq <- function(x){(-2/(x+2))+2}

ggplot(data.frame(x=c(0,20)), aes(x=x)) + 
  stat_function(fun=eq)+ xlab("Monetary Incentive")+ ylab("Participation in PMDC")+theme_bw()+ theme(axis.text.x=element_blank(),axis.text.y=element_blank(),axis.line = element_line(colour = "black"),plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank())+theme(plot.title = element_text(hjust = 0.5))

ggsave("Haas_graph.png",width = 8,height=5,units = "in")

```

## Data Preparation (Choosing Relevant Variables & Rename)

```{r data preparation}

install.packages("dplyr")
library(dplyr)

dta1 <- dplyr::select(incentive_exp,v_62,v_90,v_99, v_101,v_103,v_104,v_105,v_106,v_107, v_108,v_109,v_110)

dta2 <- dplyr::rename(dta1,
               SPP3=v_90,
               Education = v_62,
               Gender=v_99,
               Age_a=v_101,
               WTP_60a=v_103,
               WTP_60b=v_104,
               WTP_70a=v_105,
               WTP_70b=v_106,
               WTP_90a=v_107,
               WTP_90b=v_108,
               WTP_100a=v_109,
               WTP_100b=v_110
               ) 
```

## Creating Dummy Variables for 1)Age 2) Gender 3) Willingness to Particiapte (WTP) 

```{r data preparation}
## First Categorise Age into smaller group (Below 30 as 1, 30 to 50 as 2, and 50 or above as 3)
library(dplyr)
dta2<- dta2 %>% mutate(Age=case_when(Age_a<=3~ 1,Age_a >3 & Age_a<5 ~ 2, TRUE~3)) 

table(dta2$Age_a)

# Creating two dummy variables, using below 30 as the base group
dta2$Age_30_49 <- ifelse(dta2$Age==2,1,0)
dta2$Age_50_or_above <-ifelse(dta2$Age==3,1,0)

## Female Dummy 
dta2$female <- ifelse(dta2$Gender==2,1,0)

## Without High School Dummy 

dta2$without_HS <- ifelse(dta2$Education>4,0,1)

## Combining the self-learning and non-self learning experimental groups together & a binary variable for WTP. >=6: participate. <6: not participate

dta2$WTP_60c <- coalesce(dta2$WTP_60a,dta2$WTP_60b,NA)

dta2$WTP_70c <- coalesce(dta2$WTP_70a,dta2$WTP_70b, NA)

dta2$WTP_90c <- coalesce(dta2$WTP_90a,dta2$WTP_90b, NA)

dta2$WTP_100c <-coalesce(dta2$WTP_100a,dta2$WTP_100b, NA)

dta2$WTP <-coalesce(dta2$WTP_60c,dta2$WTP_70c,dta2$WTP_90c,dta2$WTP_100c,NA)

#Creating a MAX WTP Group (1: €60, 2: €70, 3: €90, 4:€100)

dta2$WTP_GRP<- NA
dta2$WTP_GRP[dta2$WTP_60c>=0]<-1
dta2$WTP_GRP[dta2$WTP_70c>=0]<-2
dta2$WTP_GRP[dta2$WTP_90c>=0]<-3
dta2$WTP_GRP[dta2$WTP_100c>=0]<-4

dta2$dummy_70 <- ifelse(dta2$WTP_GRP==2,1,0)
dta2$dummy_90 <- ifelse(dta2$WTP_GRP==3,1,0)
dta2$dummy_100 <- ifelse(dta2$WTP_GRP==4,1,0)
 
## Creating a WTP dummy 
dta2$WTP_dummy <- ifelse(dta2$WTP>=6,1,0)

## Privacy variables 
dta2$security_concern <- dta2$SPP3
dta2$security_dummy<- ifelse(dta2$SPP3>3,1,0)

## Choosing all the renamed varialbes and omited the incomplete cases

dta3<- dplyr::select(dta2,dummy_70,dummy_90,dummy_100,WTP,WTP_GRP,WTP_dummy,security_concern,security_dummy,female,Age_30_49,Age_50_or_above,without_HS) # n= 1204

dta<-na.omit(dta3)

## Provide the summary statistic table shown in appendix table 1

stargazer(as.data.frame(dta))

## Observing whether participants are randomly distributed across 4 incentive groups. 

table(dta$WTP_GRP)
```

## H1: There is an inverted U shape relationship between Monetary incentive and willingness to participate in PMDC.  

```{r}

install.packages('dotwhisker')
install.packages('dplyr')
library('dplyr')
library('dotwhisker')

m1 <- glm(WTP_dummy~dummy_70+dummy_90+dummy_100,family = binomial(link = logit), data = dta)

dwplot(m1,margins = TRUE,
       vline = geom_vline(
           xintercept = 0,
           colour = "grey60",
           linetype = 2),dot_args = list(aes(shape = model)),whisker_args = list(aes(linetype = model)))%>%relabel_predictors(
             c(dummy_70 = "€70 Incentive (ref group: €60)",
               dummy_90 = " €90 Incentive (ref group: €60)",
               dummy_100 = "€100 Incentive (ref group: €60)"
               ))+
    theme_bw(base_size = 12) + 
    xlab("Average Marginal Effects") + ylab("") +
    geom_vline(xintercept = 0,
               colour = "grey60",
               linetype = 2)+ ggtitle("Incentives on Willingness to Participate") + theme(plot.title = element_text(hjust = 0.5))+theme(
        plot.title = element_text(face = "bold"))+theme(legend.position="none")

## Output AME Table in figure 7 
ggsave("H1_logit.png",width = 9,height=6,units = "in")

## Logit Coefficient Table for H1. Appendix table 2
summary(m1)
stargazer(m1)

## Average Marginal effect table for H1: Appendix table 3 


AME_table <- margins::margins_summary(m1)


stargazer(as.data.frame(AME_table),summary = FALSE)

```

## Hypothesis 2: The more monetary incentive is offered to participants to participate in PMDC, the more concerned participants are about data privacy regarding PMDC.

````{r data analysis}

m2 <-  glm(security_dummy ~dummy_70+dummy_90+dummy_100,family = binomial(link = logit), data = dta)

summary(m2)
```

## Jitter Plots visualisation of distribution between Monetary Incentive and Security Concern

````{r data analysis}
install.packages("viridis")
library(viridis)

## What if participants security concern can be primed? Figure 8 in main analysis

whatif_a <- data.frame(Treatment = c(rep(1,300)),
                 b = c(rep(1,30),rep(2,120),rep(3,120),rep(4,30)))

whatif_b <- data.frame(Treatment = c(rep(2,30)),
                 b = c(rep(1,20),rep(2,60),rep(3,150),rep(4,70)))

whatif_c <- data.frame(Treatment = c(rep(3,300)),
                 b = c(rep(1,10),rep(2,30),rep(3,130),rep(4,130)))

whatif_d <- data.frame(Treatment = c(rep(4,300)),
                 b = c(rep(1,5),rep(2,15),rep(3,80),rep(4,200)))

what_if <- rbind(whatif_a,whatif_b,whatif_c,whatif_d)

pdf("Jitterplot1.pdf")
par(mar = c(4, 7, 4, 2) + 0.1)
plot(jitter(what_if$Treatment),
     jitter(what_if$b),
     pch = 19,
     col = viridis(1, 0.2),
     main = "If Incentives Can Prime Data Security Concern",
     font.main = 1,
     xlab = "Maximum Incentives (Euro)",
     ylab = "",
     xaxt = "n",
     yaxt = "n",
     bty = "n")
axis(1,
     at = 1:4,
     labels = c("60",
                "70",
                "90",
                "100"),
     cex.axis = 0.7)
axis(2,
     at = 1:4,
     labels = c("Not,\nConcerned at all",
                "A little,\nconcerned",
                "Somehwat,\nConcerned",
                "Very,\nConcerned"),
     las = 1,
     cex.axis = 0.7)
dev.off()

## The actual distribution of participants security concern across the foru maximum incentive group: figure 9 in main analysis

pdf("Jitterplot2.pdf")
par(mar = c(5, 6, 4, 2) + 0.1)
plot(jitter(dta$WTP_GRP),
     jitter(as.numeric(dta$security_concern)),
     pch = 19,
     col = viridis(1, 0.2),
     main = "Maximum incentive & Data Security Concern",
     font.main = 1,
     xlab = "Maximum Incentives (Euro)",
     ylab = "",
     xaxt = "n",
     yaxt = "n",
     bty = "n")
axis(1,
     at = 1:4,
     labels = c("60",
                "70",
                "90",
                "100"),
     cex.axis = 0.7)
axis(2,
     at = 1:4,
     labels = c("Not,\nConcerned at all",
                "A little,\nconcerned",
                "Somehwat,\nConcerned",
                "Very,\nConcerned"),
     las = 1,
     cex.axis = 0.7)
dev.off

`````

## H2: AME graph, logistic regressions and AME table

```{r,echo=FALSE}

## Average marginal effect graph for H2. Figure 10 in main analysis

dwplot(m2, margins = TRUE,
       vline = geom_vline(
           xintercept = 0,
           colour = "grey60",
           linetype = 2))%>% relabel_predictors(
             c(dummy_70="€70 Incentive  (ref group: €60)",
               dummy_90="€90 Incentive (ref group: €60) ",
               dummy_100= "€100 Incentive (ref group €60)"))+
    theme_bw(base_size = 12) + 
    xlab("Average Marginal Effects") + ylab("") +
    geom_vline(xintercept = 0,
               colour = "grey60",
               linetype = 2)+ ggtitle("Can Incentive Predict Data Securtiy Concern?") + theme(plot.title = element_text(hjust = 0.5))+theme(legend.position="none")

ggsave("H2_logit.png",width = 9,height=6,units = "in")


##Logistic regresison table. Appendix table 4
stargazer(m2)

## Average Marginal Effects table. Appendix table 5. 
AME_table2 <- margins::margins_summary(m2)

stargazer(as.data.frame(AME_table2),summary = FALSE)
```

H3: The effect between Incentive and WTP is mediated by the effect of security concern

## IV (€) -> DV (WTP) (Logistic Regression) (Tested in H1)
## IV (€) -> MV (Privacy Concerns) (Logistic Regression) (Tested in H2)
## IV (€) + MV (Privacy) -> DV (WTP) (Logistic Regression) (Tested in H3) 

```{r H3}
## Model

m3 <- glm(WTP_dummy~dummy_70+dummy_90+dummy_100+ security_dummy,family = binomial(link = logit), data = dta)

m4 <- glm(WTP_dummy~dummy_70+dummy_90+dummy_100+security_dummy+Age_30_49+Age_50_or_above+ female+without_HS,family = binomial(link = logit), data = dta)

```

## H3: AME graph, logistic regression table, AME table

```{r visualisation}

dwplot(list(m3,m4), margins = TRUE,
       vline = geom_vline(
           xintercept = 0,
           colour = "grey60",
           linetype = 2),dot_args = list(aes(shape = model)),whisker_args = list(aes(linetype = model)))%>% relabel_predictors(
             c(dummy_70="€70 Incentive  (ref group: €60)",
               dummy_90="€90 Incentive (ref group: €60) ",
               dummy_100= "€100 Incentive (ref group €60)",
               security_dummy="High security concern",
               Age_30_49="Age (30-49)",
               Age_50_or_above="Age (50 or above)",
               female= "Female",
               without_HS="Without HS degree"))+theme_bw(base_size = 12) + 
    xlab("Average Marginal Effects") + ylab("") +
    geom_vline(xintercept = 0,
               colour = "grey60",
               linetype = 2)+ ggtitle("Is Data Security Concern a Mediator?") + theme(plot.title = element_text(hjust = 0.5))+ guides(color = guide_legend(order = 1),
         size = guide_legend(order = 2),
         shape = guide_legend(order = 3))+theme(
        plot.title = element_text(face = "bold"),
        legend.position = "right",
        legend.justification = c(0, 0),
        legend.background = element_rect(colour = "grey80"),
        legend.title.align = .5
    ) +guides(shape = guide_legend("Model"), colour = guide_legend("Model"))+ scale_colour_discrete(name = "Model", labels = c("Baseline", "With Controls"))+scale_shape(name = "Model", labels = c("Baseline", "With Controls"))

ggsave("H3_logit.png",width = 9,height=6,units = "in")

#Logsitic regression tables: Appendix table 6
summary(m3)
summary(m4)
stargazer(list(m3,m4))

##Average Marginal effect table for m3: Appendix table 7, m4: appendix table 8. 

AME_table3 <- margins::margins_summary(m3)

stargazer(as.data.frame(AME_table3),summary = FALSE)

AME_table4 <- margins::margins_summary(m4)

stargazer(as.data.frame(AME_table4),summary = FALSE)

```

Sub-Group Analysis I: Data Preparation 

```{r}
library(ggplot2)
library(dplyr)
library(dotwhisker)
## Select Variables 
SGA1 <- dplyr::select(incentive_exp,v_111,v_113, v_114)
## Rename 
SGA<-  dplyr::rename(SGA1,With_100 =v_111,
                More=v_113,
                Never = v_114)
```

Sub Group Analysis I: How Much Extra Money is needed? (Discussion + Appendix 6 and 7)

```{r}

## Exclude those who are offered €100 originally AND those who are willing to participate.
## Only Offered less  than €100 and unwilling to participate is left
Below100_XWTP <- SGA[complete.cases(SGA[,1]),]

Below100_XWTP$correct <- ifelse(Below100_XWTP$More>0 & Below100_XWTP$Never==1,888)
Below100_XWTP$correct[is.na(Below100_XWTP$correct)] <- 0

SGA_I <- subset(Below100_XWTP, correct<888)
 
## How many people are willing to participate with just €100 and €100 is not enough
SGA_I$extra[SGA_I$With_100==1]<- "Yes to €100"
SGA_I$extra[SGA_I$With_100==2]<- "No to €100"

table(SGA_I$extra)

SGA_I$NEW <- coalesce(SGA_I$More,SGA_I$Never,NA)

## Create a new variable that label the responses 

SGA_I$NEW2[SGA_I$NEW==1]<- "Will not participate with more money"
SGA_I$NEW2[SGA_I$NEW>1]<- "Will participate with more money"

## Excluding non-responses for this question -> (N=220)
SGAI_a<- SGA_I[complete.cases(SGA_I[,6]),]

table(SGAI_a$NEW2)

## Only selecting those who want incentive more than €100.  (N=79)

More_Never<- subset(SGA_I, More >100)

More_Never$NEW <- coalesce(More_Never$More,More_Never$Never,NA)

More_Never$NEW2[More_Never$NEW==1]<- "Will not participate with more money"
More_Never$NEW2[More_Never$NEW>1]<- "Will participate with more money"

median(More_Never$More)

```

## Visualising the median

```{r}
ggplot(More_Never, aes(x=NEW))+geom_histogram(binwidth = 25)+ scale_x_continuous(breaks = scales::pretty_breaks(n = 10))+ geom_density(alpha=.2, fill="#FF6666") +geom_vline(aes(xintercept=median(NEW),color="median"), linetype="dashed")+labs(title="",x="Incentive (€)",y = "Frequency")+theme(plot.title = element_text(hjust = 0.5))+  scale_color_manual(name = "Statistics", values = c(median = "blue"))

ggsave("How_much_more.png",width = 9,height=6,units = "in")

```

Sub Group Analysis II: Will participants still participate with less money than offered? If so, is it because of non-monetary reasons? (Appendix Figure 8).

```{r}
library(ggplot2)
## THose offered more than 60 and willing to participate 

SGA2a <- dplyr::select(incentive_exp,v_112)

SGA2b<-  dplyr::rename(SGA2a,With_60 =v_112)

SGA2 <- na.omit(SGA2b)

SGA2$Answers <- ifelse(SGA2$With_60==2,0,1)

SGA2$Answers[SGA2$Answers==1]<- 'Ok with €60'
SGA2$Answers[SGA2$Answers==0]<- 'Not Okay with €60'

ggplot(SGA2, aes(x=Answers)) + geom_histogram(binwidth = 1,stat = "count")+  labs(title="Will you participate if offered only €60? (n= 503)",x="",y = "Frequency")+theme(plot.title = element_text(hjust = 0.5))+ geom_bar(aes(fill = Answers))+ geom_text(stat='count', aes(label=..count..), vjust=1)+scale_fill_discrete(name="")+  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank() 
        )+theme(legend.position="bottom")

ggsave("Okay_with_60.png",width = 9,height=6,units = "in")
```

Appendix: Distribution of Willingness to participate (Appendix Figure 1-5)

```{r}
## Aggregate WTP 

ggplot(dta, aes(x=WTP)) + geom_histogram(binwidth = 0.5)+  labs(title="Willingness to Participate (N=1204)",x="Willingness to Participate", y = "Count")+scale_x_continuous(breaks = seq(0, 10, by = 1))+theme(plot.title = element_text(hjust = 0.5))

ggsave("WTP_AGG.png",width = 9,height=6,units = "in")

## 60 Incentives 

WTP_60_h <- subset(dta, WTP_GRP==1)

ggplot(WTP_60_h, aes(x=WTP)) + geom_histogram(binwidth = 0.5)+  labs(title="Willingness to Participate €60 Group (n= 296)",x="Willingness to Participate", y = "Count")+scale_x_continuous(breaks = seq(0, 10, by = 1))+theme(plot.title = element_text(hjust = 0.5))

ggsave("WTP_60.png",width = 9,height=6,units = "in")

WTP_70_h <- subset(dta, WTP_GRP==2)

ggplot(WTP_70_h, aes(x=WTP)) + geom_histogram(binwidth = 0.5)+  labs(title="Willingness to Participate €70 Group (n= 300)",x="Willingness to Participate", y = "Count")+theme(plot.title = element_text(hjust = 0.5))+ scale_x_continuous(breaks = scales::pretty_breaks(n = 10))

ggsave("WTP_70.png",width = 9,height=6,units = "in")

WTP_90_h <- subset(dta, WTP_GRP==3)

ggplot(WTP_90_h, aes(x=WTP)) + geom_histogram(binwidth = 0.5)+  labs(title="Willingness to Participate €90 Incentive Group  (n= 301)",x="Willingness to Participate", y = "Count")+theme(plot.title = element_text(hjust = 0.5))+ scale_x_continuous(breaks = scales::pretty_breaks(n = 10))

ggsave("WTP_90.png",width = 9,height=6,units = "in")

WTP_100_h <- subset(dta, WTP_GRP==4)

ggplot(WTP_100_h, aes(x=WTP)) + geom_histogram(binwidth = 0.5)+  labs(title="Willingness to Participate €100 Incentive Group (n= 307)",x="Willingness to Participate", y = "Count")+theme(plot.title = element_text(hjust = 0.5))+ scale_x_continuous(breaks = scales::pretty_breaks(n = 10))

ggsave("WTP_100.png",width = 9,height=6,units = "in")

```

Appendix: Different opeerationalizations of Willingness to Participate (Table 9)

```{r Appendix Stuff}
dta_appendix <- dplyr::select(dta,dummy_70,dummy_90,dummy_100,WTP,WTP_GRP,security_concern,security_dummy,female,Age_30_49,Age_50_or_above,without_HS)

## WTP_dummy with different cutpoint: Dummy 2: 0-4: unwilling, 5-10 willing, Dummy 3: only use extreme points (0:unwilling, 1: willing)  

dta_appendix$WTP_Dummy <-ifelse(dta_appendix$WTP>=6,1,0)
dta_appendix$WTP_Dummy2 <-ifelse(dta_appendix$WTP>=5,1,0)
dta_appendix$WTP_Dummy3 <- NA 
dta_appendix$WTP_Dummy3[dta_appendix$WTP==10]<-1
dta_appendix$WTP_Dummy3[dta_appendix$WTP==0]<-0

## The logistic regressions for hypothesis 1 and hypothesis 3 with different cutoff 
m1_APP<- glm(WTP_Dummy2~dummy_70+dummy_90+dummy_100,family = binomial(link = logit), data = dta_appendix)

m3_APP <- glm(WTP_Dummy2~dummy_70+dummy_90+dummy_100+security_dummy,family = binomial(link = logit), data = dta_appendix)

m4_APP<- glm(WTP_Dummy2~dummy_70+dummy_90+dummy_100+security_dummy+Age_30_49+Age_50_or_above+female+without_HS,family = binomial(link = logit), data = dta_appendix)

## The logistic regressions for hypothesis 1 and hypothesis 3 with just extreme points

m1_APP2<- glm(WTP_Dummy3~dummy_70+dummy_90+dummy_100,family = binomial(link = logit), data = dta_appendix)

m3_APP2 <- glm(WTP_Dummy3~dummy_70+dummy_90+dummy_100+security_dummy,family = binomial(link = logit), data = dta_appendix)

m4_APP2<- glm(WTP_Dummy3~dummy_70+dummy_90+dummy_100+security_dummy+Age_30_49+Age_50_or_above+female+without_HS,family = binomial(link = logit), data = dta_appendix)

## Regression table: Appendix table 9 
stargazer(m1_APP,m3_APP,m4_APP,m1_APP2,m3_APP2,m4_APP2)
```

Appendix: different operationalisation of security concern using the original 4 point scale. (Table 10)

````{r}
## Using the 4-scale security concern variable

m3_APP3 <- glm(WTP_Dummy~dummy_70+dummy_90+dummy_100+security_concern,family = binomial(link = logit), data = dta_appendix)

m4_APP3<- glm(WTP_Dummy~dummy_70+dummy_90+dummy_100+security_concern+Age_30_49+Age_50_or_above+female+without_HS,family = binomial(link = logit), data = dta_appendix)

## Visualisation: Appendix table 10 

stargazer(m3_APP3,m4_APP3)
```